taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_appA.Rnw
appendices as standalone .Rnw/.tex minor fixes

\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

<<thespecieslist, eval=TRUE>>=
splist <- c("Helanthus annuus", "Pinos contorta", "Collomia grandiflorra", "Abies magnificaa", 
  	"Rosa california", "Datura wrighti", "Mimulus bicolour", "Nicotiana glauca",
		"Maddia sativa", "Bartlettia scapposa")
@

@@

# Make a map
p <- gbifmap(occurr_list) + 
  guides(col = guide_legend(title="", nrow = 3, byrow = TRUE)) + 
  theme(legend.position="bottom", legend.key = element_blank()) +
  coord_equal() 
p
@

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

\begin{document}
<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment='#')
@

\renewcommand\thefigure{A.\arabic{figure}}    
\setcounter{figure}{0}

\section*{Appendix A. A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

<<thespecieslist, eval=TRUE>>=
splist <- c("Helanthus annuus", "Pinos contorta", "Collomia grandiflorra", "Rosa california", "Mimulus bicolour", "Nicotiana glauca", "Maddia sativa")
@

@@

# Make a map
p <- gbifmap_list(occurr_list) + 
  guides(col = guide_legend(title="", nrow = 3, byrow = TRUE)) + 
  theme(legend.position="bottom", legend.key = element_blank()) +
  coord_equal() 
p
@
\end{document}

### 2013-10-01 f1000_rev/taxize_appC.tex
appendices as standalone .Rnw/.tex minor fixes

\section*{Installation of the development version of taxize and API keys}

@@

<<installcran, eval=FALSE>>=
install.packages("taxize")
library(taxize)
@

@@

<<checkdevtools, eval=FALSE>>=
library(devtools)
has_devel()
@

@@

<<install, eval=FALSE>>=
install_github("taxize_", "ropensci")
@

@@

<<load, eval=FALSE>>=
library(taxize)
@

@@

<<openrprofile, engine='bash', eval=FALSE>>=
open .Rprofile
@

@@

<<writerprofile, engine='bash', eval=FALSE>>=
# uBio API key
options(uBioApi = "youralphanumerickey")
@

@@

\begin{itemize}
  \item \emph{uBio}: ubio\_namebank
  \item \emph{EOLApi}: eol\_dataobjects, eol\_hierarchy, eol\_pages, eol\_ping, eol\_search
  \item \emph{tropicoskey}: tp\_acceptednames, tp\_namedistributions, tp\_namereferences, tp\_summary, tp\_synonyms
  \item \emph{pmkey}: plantminer
\end{itemize}

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography]{revtex4-1}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\section*{Appendix C. Installation of the development version of taxize and API keys}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install.packages}\hlstd{(}\hlstr{"taxize"}\hlstd{)}
\hlkwd{library}\hlstd{(taxize)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\hlkwd{has_devel}\hlstd{()}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install_github}\hlstd{(}\hlstr{"taxize_"}\hlstd{,} \hlstr{"ropensci"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(taxize)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
open .Rprofile
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
# uBio API key
options(uBioApi = "youralphanumerickey")
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{itemize}
  \item \emph{uBio}: ubio\_namebank
  \item \emph{EOLApi}: eol\_dataobjects, eol\_hierarchy, eol\_pages, eol\_ping, eol\_search
  \item \emph{tropicoskey}: tp\_acceptednames, tp\_namedistributions, tp\_namereferences, tp\_summary, tp\_synonyms
  \item \emph{pmkey}: plantminer
\end{itemize}
\end{document}
